\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{fancybox}
\usepackage[most]{tcolorbox}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeTwoSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
       \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% my custom command for link buttons
\newcommand{\linkbutton}[2]{%
  \href{#1}{%
    \tcbox[
      on line,
      enhanced,
      colback=gray!20,
      boxrule=0pt,      
      arc= 5pt,        
      boxsep=0pt,
      left=4pt,
      right=4pt,
      top=2.5pt,
      bottom=2.5pt
    ]{%
      \footnotesize\sffamily\fontseries{m}\selectfont #2%
    }%
  }%
}

\hypersetup{
  colorlinks=false,
  pdfborder={0 0 0}
}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{\Large Benson (Yanbo) Xiao}\\[4pt]
  \small
  Waterloo, ON $\cdot$
  \href{mailto:bensonxiao0721@gmail.com}{bensonxiao0721@gmail.com}\\[0pt]
  \linkbutton{https://github.com/TractorBenson}{GitHub} 
  \linkbutton{https://linkedin.com/in/yanbo-xiao}{LinkedIn} 
  \linkbutton{https://bensonxiao.me}{bensonxiao.me}
\end{center}

%--------SKILLS------------
\section{Skills}
\begin{itemize}[leftmargin=*]

  \item \textbf{Languages}: C/C++, Python, JavaScript/TypeScript, HTML/CSS, Bash
  \item \textbf{Frameworks \& Libraries}: Next.js, Tailwind CSS, Node.js, Flask, Chart.js, Discord.js, Octokit.js
  \item \textbf{Tools \& Platforms}: Git, Docker, Docker Compose, Drone CI, Linux, X11, Nginx, Caddy

\end{itemize}


% -----------Experience-----------------
\section{Experience}
\resumeSubHeadingListStart

  \resumeTwoSubheading
    {Customer Support Agent - Windscribe}{Sep -- Dec 2025}
    {Windscribe Limited}{Remote}
    \resumeItemListStart
      \resumeItem{Network Troubleshooting}{Applied networking fundamentals (\textbf{networking protocols}, \textbf{DNS}) to diagnose and resolve VPN connectivity issues; configured virtual machines to reproduce and test client-side failures.}
      \resumeItem{Automation Tooling}{Designed and implemented a \textbf{JavaScript browser extension} to automate high-frequency support operations, reducing average task completion time by \textbf{80\%}.}
    \resumeItemListEnd
  
\resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

% --- WWP ---
\resumeSubheading
  {WhoWillPay Expense Tracker 
  \linkbutton{https://github.com/20age1million/who-will-pay-expense-tracker}{GitHub} 
  % \linkbutton{https://wwp.20age1million.com/}{Demo} // Demo currently down
  }{Feb -- Apr 2025}
  \resumeItemListStart
    \resumeItem{Algorithm}{Implemented weighted random payer selection (O(n)) with \textbf{Python}; reduced payer-decision clicks from 10 to \textbf{1}, turning 3-min discussions into a 2-second button press.}
    \resumeItem{Visualization}{Integrated a \textbf{Chart.js}-based dashboard (pie chart) with responsive UI; maintained \textbf{80 ms} average API latency.}
    \resumeItem{Backend}{Built RESTful APIs using \textbf{Flask} backed by a \textbf{SQLite} schema to manage user expenses with consistent data integrity.}
  \resumeItemListEnd

% --- GIToday ---
\resumeSubheading
  {GIToday Discord Bot \linkbutton{https://github.com/20age1million/GIToday}{GitHub}}{Sep -- Dec 2025}
  \resumeItemListStart
    \resumeItem{Bot Development}{Developed a Discord bot in \textbf{TypeScript} and \textbf{Node.js} using \textbf{Discord.js} to automatically deliver daily GitHub activity reports to organization channels.}
    \resumeItem{Data Aggregation}{Collected and processed commit activity from the \textbf{GitHub} API using \textbf{Octokit.js} to rank contributors within a GitHub organization over a rolling 24-hour window.}
    \resumeItem{API Orchestration}{Orchestrated multiple \textbf{third-party APIs} (GitHub, Discord, OpenAI) to generate and publish structured, readable summaries without manual intervention.}
  \resumeItemListEnd

% --- CI/CD Automation Platform ---
\resumeSubheading
  {CI/CD Automation with Drone \& Docker}{Sep -- Oct 2025}
  \resumeItemListStart
    \resumeItem{CI Workflow}{Configured and used \textbf{Drone} CI pipelines integrated with \textbf{Git} repositories to trigger automated builds on push and merge events.}  
    \resumeItem{Containerization}{Used \textbf{Docker} and \textbf{Docker Compose} to build and run containerized services, ensuring consistent environments across development and deployment.}
    \resumeItem{Infrastructure Management}{Managed containerized services and deployment configurations through \textbf{1Panel}, including service control and environment management.}
  \resumeItemListEnd

% --- CS246 Chess ---
\resumeSubheading
  {C++ Chess \linkbutton{https://github.com/TractorBenson/Chess}{GitHub}}{Jul -- Aug 2025}
  \resumeItemListStart
    \resumeItem{Systems \& Graphics}{Built a chess game in \textbf{C++20} using low-level \textbf{X11} graphics, implementing a custom rendering loop without external game engines.}
    \resumeItem{Architecture \& Events}{Developed modular game logic and an event-driven input pipeline, separating game state, move execution, and rendering for maintainable gameplay flow.}
  \resumeItemListEnd

% --- GreenGroup ---
\resumeSubheading
  {GreenGroup Web Page \linkbutton{https://greengroup.20age1million.com/}{GitHub} \linkbutton{https://greengroup.20age1million.com/}{Demo}}{Dec 2025}
  \resumeItemListStart
    \resumeItem{Frontend UI}{Built a style-focused web page using \textbf{Next.js} with its file-based routing system, implementing responsive layouts and page navigation.}
    \resumeItem{Styling}{Designed and refined the UI using \textbf{Tailwind CSS}, emphasizing visual consistency, spacing, and reusable utility-based styles.}
  \resumeItemListEnd



\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\begin{itemize}[leftmargin=*]

  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{University of Waterloo} & Waterloo, ON \\
      Honours Bachelor of Computer Science & Sep 2024 – Apr 2029 (expected) \\
    \end{tabular*}

\end{itemize}

 
% %--------RELEVANT COURSES------------
% \section{Relevant Courses}
%   \resumeSubHeadingListStart
%     \resumeTwoSubheading{CS 246}{Spring 2025}{Object-Oriented Software Development}{}
%     \resumeTwoSubheading{CS 146}{Winter 2025}{Elementary Algorithm Design and Data Abstraction (Advanced Level)}{}
%     \resumeTwoSubheading{CS 145}{Fall 2024}{Designing Functional Programs (Advanced Level)}{}
    
%   \resumeSubHeadingListEnd

% %-------------------------------------------
\end{document}
